\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
more text for online survey
added some todo's need to generate figures and collect math

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. The analysis of these results will be done in Section~\ref{sec:analysis}.

@@

>>>>

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once.The analysis of these results will be done in Section~\ref{sec:analysis}.

\todo Write demographic questions and compensation

\todo Write about survey participants

\todo Write about control question

\todo Write about satisficing control and concerns

@@

\subsection{Feature Design for Trajectory Classification}

\todo

Write about:
\begin{itemize}
\item clearance
\item smoothness
\item hausdorff distance
\item dynamic time warping
\item angular distance
\item path length
\item bfs path computation
\item figures for examples of high-low values of the above
\end{itemize}
\todo
